Packaging research artifacts with RO-Crate

### 2021-05-03 latex/ro-crate.tex
More latex settings..

% add. options: [seceqn,secthm,crcready]
\documentclass[ds]{iosart2x}
\usepackage[utf8]{inputenc}
\usepackage[smartEllipses,tableCaptions,pipeTAbles,fencedCode,footnotes,underscores]{markdown}
\def\markdownOptionOutputDir{../output}

@@

@@

\markdownInput{../content/10.background.md}
\markdownInput{../content/20.rocrate.md}
\markdownInput{../content/21.conceptual.md}
\markdownInput{../content/22.implementation.md}
\markdownInput{../content/23.community.md}
\markdownInput{../content/30.tooling.md}
\markdownInput{../content/40.inuse.md}
\markdownInput{../content/50.relatedwork.md}
\markdownInput{../content/60.conclusion.md}
%\markdownInput{../content/80.formal-definition.md}

>>>>

% add. options: [seceqn,secthm,crcready]
\documentclass[ds]{iosart2x}
%\usepackage[utf8]{inputenc}

% From https://www.overleaf.com/latex/templates/using-the-stix2-opentype-fonts-with-lualatex-or-xelatex/hdfvhzqmhnpx
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{fontspec}
\usepackage{unicode-math}
\usepackage{graphicx}

%%

\DeclareGraphicsExtensions{.png,.pdf}
\graphicspath{../content/images/}
\usepackage[smartEllipses,tableCaptions,pipeTables,fencedCode,footnotes,underscores,hybrid]{markdown}
\def\markdownOptionOutputDir{../output}

@@

\setmathfont{STIX2Math}[
Extension={.otf},
Path=./STIX2fonts/,
Scale=1]
\setmainfont{STIX2Text}[
Extension={.otf},
Path=./STIX2fonts/,
UprightFont={*-Regular},
BoldFont={*-Bold},
ItalicFont={*-Italic},
BoldItalicFont={*-BoldItalic}]

@@

\markdownInput{../content/10.background.md}
\markdownInput{../content/20.rocrate.md}
\markdownInput{../content/21.conceptual.md}
\markdownInput{../content/22.implementation.md}
\markdownInput{../content/23.community.md}
\markdownInput{../content/30.tooling.md}
\markdownInput{../content/40.inuse.md}
\markdownInput{../content/50.relatedwork.md}
\markdownInput{../content/60.conclusion.md}
\markdownInput{../content/80.formal-definition.md}
